Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-07-09 Documents/Paper/ms.tex
sentence
Pareto
Pareto stuff
GalaxyField hyperparameters

\begin{document}
\maketitle
\abstract{This is the abstract.}

@@

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
%\section{``Galaxy Field'' Example}

>>>>

\begin{document}
\maketitle
\abstract{Blah...
We demonstrate the techniques on a seemingly simple problem of detecting
sinusoidal signals in noise, which exhibits a phase transition.}

@@

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
\section{``Galaxy Field'' Example}

We model each galaxy as a mixture of two concentric elliptical galaxies, with
the following eight parameters. Firstly, two
parameters $x_c$ and $y_c$ describe the central position of the galaxy within
the image. The flux $f$ describes the total integral of the galaxy's
intensity profile. The axis ratio $q$ describes the ellipticity of the galaxy
and $\theta$ its orientation angle with respect to horizontal. Finally
we include a ``radius ratio'' $u$ describing the ratio of the radius of the
smaller gaussian with respect to that of the bigger gaussian, and a parameter
$v$ describing the fraction of the total flux in the outer gaussian
(therefore the fraction of the light in the smaller gaussian is $1-f$).

For the interim prior for the total fluxes of the galaxies, and for the
widths of the galaxies, we use the Pareto
distribution. The probability density function for a variable $x$ given
hyperparameters $x_{\rm min}$ and $a$ is
\begin{eqnarray}
p(x | x_{\rm min}, a) &=&
\left\{
\begin{array}{lr}
\frac{a x_{\rm min}^{a}}{x^{a + 1}}, & x \geq x_{\rm min}\\
0, & \textnormal{otherwise.}
\end{array}
\right.
\end{eqnarray}
Since we are using this for both the fluxes and the widths of the galaxies,
there will be four hyperparameters in total for the fluxes and widths.

% Pareto in terms of log(x)
% p(x) ~ x^(-(alpha + 1))
% Let u = log(x), du = 1/x dx
% p(u) = e^(-alpha*u)
